The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-06-22 ms.tex
Finish section 2 and the 3D figure caption

\section{Longslit Spectroscopy}
\label{sec:observations}

@@

Figure~\ref{fig:pv-array} shows the position-velocity arrays of (left-to-rght)
\Ha{} \Wav{6563}, \nii{} \Wav{6583}, and \oiii{} \Wav{5007} for the 11 individual positions from the 2015 run.
The velocity scale is heliocentric 
and the scale along the slit is specified as arcsecond offsets from the central star.
% We derive a heliocentric
% systemic velocity, \(\vsys = \SI{40}{km.s^{-1}}\) by using the slit position F (epoch 2003) that passes through the central star and is not saturated. 
An additional slit (X, shown in Figure~\ref{fig:halo-knots}) was placed on the northern outskirts of the nebula 
in the outer halo of NGC~6210 where filaments had been clearly detected in some of our deep images.
% The observation was carried out on 18 September 2019.  The spectrum was obtained in order 87 (\Ha{} and \nii lines) with the 150 micron slit oriented at a position angle of 56 degrees.  The detector was again the Marconi 2048x2048 with a 3$\times$3 binning.  The spectral dispersion was 0.087 \AA/pix and 0.525\arcsec/pixel.

Most of the spectra presented here are included in the \mbox{San Pedro Mártir} Kinematic Catalogue of Galactic Planetary Nebulae\footnote{
  \url{http://kincatpn.astrosen.unam.mx}
}
and are publicly available as pdf or fits files
\citep{Lopez:2012a}.

 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{tere-figs/Figure2a}
  \caption{Top panel shows the slit positions from the 2015 run, these are indicated as solid lines and 
labeled at the top against an [O III] HST image. Dashed lines refer to additional slit positions from other runs
and are labeled at the bottom of the image. The middle and bottom panels show the slit positions from 
the other runs placed at different position angles. }
  \label{fig:slit-positions}
\end{figure}

All data was reduced  by using standard IRAF\footnote{IRAF is
  distributed by the National Optical Astronomy Observatory, which is
  operated by the Association of Universities for Research in
  Astronomy, Inc. under cooperative agreement with the National
  Science foundation} routines.
Bias and cosmic-ray removal was followed by rectification and first-order wavelength 
calibration of the two-dimensional spectra
based on the comparison the spectrum
of a Th/Ar lamp to an accuracy of $\pm$1 \kms{} when converted to radial velocity.
All spectra presented in this paper are corrected to heliocentric velocity (\vhel).

@@

\begin{figure*}
  \includegraphics[width=\linewidth]
  {figs/cut-axis-4panel}
  \caption{Three dimensional reconstruction of the nebular structure and kinematics. }
  \label{fig:cut-axis-3d}
\end{figure*}

>>>>

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{tere-figs/Figure2a}
  \caption{Top panel shows the slit positions from the 2015 run, these are indicated as solid lines and 
labeled at the top against an [O III] HST image. Dashed lines refer to additional slit positions from other runs
and are labeled at the bottom of the image. The middle and bottom panels show the slit positions from 
the other runs placed at different position angles. }
  \label{fig:slit-positions}
\end{figure}

@@

All data was reduced using standard IRAF\footnote{IRAF is
  distributed by the National Optical Astronomy Observatory, which is
  operated by the Association of Universities for Research in
  Astronomy, Inc. under cooperative agreement with the National
  Science foundation} routines.
Bias and cosmic-ray removal was followed by rectification and first-order wavelength 
calibration of the two-dimensional spectra
based on the comparison spectrum
of a Th/Ar lamp, yielding an accuracy in velocity units of \SI{\pm 1}{km.s^{-1}}.
Figure~\ref{fig:pv-array} shows example position-velocity arrays of (left-to-right)
\Ha{} \Wav{6563}, \nii{} \Wav{6583}, and \oiii{} \Wav{5007} for the 11 individual positions from the 2015 run.
The velocity scale is heliocentric 
and the scale along the slit is specified as arcsecond offsets from the central star.
% We derive a heliocentric
% systemic velocity, \(\vsys = \SI{40}{km.s^{-1}}\) by using the slit position F (epoch 2003) that passes through the central star and is not saturated. 
An additional slit (X, shown in Figure~\ref{fig:halo-knots}) was placed on the northern outskirts of the nebula 
in the outer halo of NGC~6210 where filaments had been clearly detected in some of our deep images.\footnote{For this spectrum only, \(3 \times 3\) pixel on-chip binning was used.}
% The observation was carried out on 18 September 2019.  The spectrum was obtained in order 87 (\Ha{} and \nii lines) with the 150 micron slit oriented at a position angle of 56 degrees.  The detector was again the Marconi 2048x2048 with a 3$\times$3 binning.  The spectral dispersion was 0.087 \AA/pix and 0.525\arcsec/pixel.
Most of the spectra presented here are publicly available from the \mbox{San Pedro Mártir} Kinematic Catalogue of Galactic Planetary Nebulae\footnote{
  \url{http://kincatpn.astrosen.unam.mx}
}
\citep{Lopez:2012a}.

@@

\begin{figure*}
  \includegraphics[width=\linewidth]
  {figs/cut-axis-4panel}
  \caption{
    Three dimensional reconstruction of the nebular structure and kinematics,
    assuming all outflows are strictly radial.
    Panels (a), (b), and (c) show cut planes containing the line of sight
    and the symmetry axes of the shells and lobes.
    Some small artistic license is taken, since axis A and C are not strictly coplanar with the line of sight.
    Knots and knot complexes do not share these axes, but are also shown projected onto the closest planes.
    Arrows show the magnitude and direction of the derived three-dimensional velocity of each feature.
    Faint gray dashed lines for Outer lobe system \SysM{2} show the range of possibilities for this feature given that no proper motions are available for it.
  }
  \label{fig:cut-axis-3d}
\end{figure*}
